### 2019-12-16 tex/ms.tex
section about EXPTIME; other edits

Before we can compare on-sky GFA measurements to our predicted zeropoint, we need to have accurate knowledge of how to convert from ADU (units of the raw GFA data) to electrons. Lab-measured GFA gains are available in a series of DESI DocDB entries, and a set of Mayall dome screen data were also taken specifically to enable post-installation gain measurements on 20191027. My gain measurements from the post-installation dome screen data are documented on the DESI wiki\footnote{\url{https://desi.lbl.gov/trac/wiki/Commissioning/Planning/gfachar/gain_20191027}}. The lab measurements and my dome screen measurements are listed in Table \ref{tab:gains}.

@@

My gain measurements based on the 20191027 dome screen data are $\sim$0.9\% higher than the corresponding lab gain measurements in the median. David Kirkby has also analyzed the same 20191027 dome screen data and was able to obtain even better agreement with the lab gain measurements (DESI-5315). We therefore adopt the lab gain measurements compiled from the various GFA acceptance reports when comparing out predicted zeropoint to the on-sky measurements. It seems clear that we should not expect our knowledge of the gains to be a significant limitation in the comparison between measured and predicted zeropoints.

@@

@@

@@

\begin{center}
\begin{table}[ht]
\begin{tabular}{c | c | c | c | c}
camera & amp & ZP (total raw ADU/s) & ZP (total e-/s) & assumed gain (e-/ADU, acceptance report) \\ \hline
GUIDE0 & E & 25.714 & 27.079 & 3.516 \\
GUIDE0 & F & 25.689 & 27.063 & 3.545 \\
GUIDE0 & G & 25.654 & 27.067 & 3.673 \\
GUIDE0 & H & 25.695 & 27.078 & 3.574 \\
GUIDE2 & E & 25.633 & 27.045 & 3.668 \\
GUIDE2 & F & 25.612 & 27.035 & 3.708 \\
GUIDE2 & G & 25.654 & 27.067 & 3.673 \\
GUIDE2 & H & 25.627 & 27.057 & 3.733 \\
GUIDE3 & E & 25.652 & 27.063 & 3.669 \\
GUIDE3 & F & 25.679 & 27.058 & 3.560 \\
GUIDE3 & G & 25.615 & 27.061 & 3.785 \\
GUIDE3 & H & 25.623 & 27.052 & 3.729 \\
GUIDE5 & E & 25.626 & 27.052 & 3.718 \\
GUIDE5 & F & 25.630 & 27.062 & 3.741 \\
GUIDE5 & G & 25.636 & 27.066 & 3.733 \\
GUIDE5 & H & 25.621 & 27.066 & 3.787 \\
GUIDE7 & E & 25.569 & 27.036 & 3.863 \\
GUIDE7 & F & 25.664 & 27.063 & 3.629 \\
GUIDE7 & G & 25.494 & 27.011 & 4.043 \\
GUIDE7 & H & 25.512 & 27.008 & 3.967 \\
GUIDE8 & E & 25.615 & 27.047 & 3.740 \\
GUIDE8 & F & 25.601 & 27.048 & 3.793 \\
GUIDE8 & G & 25.699 & 27.090 & 3.601 \\
GUIDE8 & H & 25.652 & 27.072 & 3.698 \\
\end{tabular}
\caption{zeropoint results}
\label{tab:zps}
\end{table}
\end{center}

@@

@@

>>>>

Before we can compare on-sky GFA measurements to our predicted zeropoint, we need to have accurate knowledge of how to convert from ADU (units of the raw GFA data) to electrons. Lab-measured GFA gains are available in a series of DESI DocDB entries (see Table \ref{tab:gains}), and a set of Mayall dome screen data were also taken on 20191027 specifically to enable post-installation gain measurements. My gain measurements from the post-installation dome screen data are documented on the DESI wiki\footnote{\url{https://desi.lbl.gov/trac/wiki/Commissioning/Planning/gfachar/gain_20191027}}. The lab measurements and my dome screen measurements are listed in Table \ref{tab:gains}.

@@

My gain measurements based on the 20191027 dome screen data are in very good agreement with those based on the lab data, although the former are $\sim$0.9\% higher than the corresponding lab gain measurements in the median. David Kirkby has also analyzed the same 20191027 dome screen data and was able to obtain even better agreement with the lab gain measurements (DESI-5315). We therefore adopt the lab gain measurements compiled from the various GFA acceptance reports when comparing our predicted zeropoint to the on-sky measurements. It seems clear that we should not expect our knowledge of the gains to be a significant limitation in the comparison between measured and predicted zeropoints.

@@

For this study, we use a series of 22 exposures

% check the 22 value above...

@@

Table \ref{tab:zps} lists the zeropoint values obtained in terms of both ADU/s and e-/s on a per-amp basis for all six guide GFA cameras.

@@

\begin{center}
\begin{table}[ht]
\begin{tabular}{c | c | c | c | c}
camera & amp & ZP (total raw ADU/s) & ZP (total e-/s) & assumed gain (e-/ADU, acceptance report) \\ \hline
GUIDE0 & E & 25.714 & 27.079 & 3.516 \\
GUIDE0 & F & 25.689 & 27.063 & 3.545 \\
GUIDE0 & G & 25.654 & 27.067 & 3.673 \\
GUIDE0 & H & 25.695 & 27.078 & 3.574 \\
GUIDE2 & E & 25.633 & 27.045 & 3.668 \\
GUIDE2 & F & 25.612 & 27.035 & 3.708 \\
GUIDE2 & G & 25.654 & 27.067 & 3.673 \\
GUIDE2 & H & 25.627 & 27.057 & 3.733 \\
GUIDE3 & E & 25.652 & 27.063 & 3.669 \\
GUIDE3 & F & 25.679 & 27.058 & 3.560 \\
GUIDE3 & G & 25.615 & 27.061 & 3.785 \\
GUIDE3 & H & 25.623 & 27.052 & 3.729 \\
GUIDE5 & E & 25.626 & 27.052 & 3.718 \\
GUIDE5 & F & 25.630 & 27.062 & 3.741 \\
GUIDE5 & G & 25.636 & 27.066 & 3.733 \\
GUIDE5 & H & 25.621 & 27.066 & 3.787 \\
GUIDE7 & E & 25.569 & 27.036 & 3.863 \\
GUIDE7 & F & 25.664 & 27.063 & 3.629 \\
GUIDE7 & G & 25.494 & 27.011 & 4.043 \\
GUIDE7 & H & 25.512 & 27.008 & 3.967 \\
GUIDE8 & E & 25.615 & 27.047 & 3.740 \\
GUIDE8 & F & 25.601 & 27.048 & 3.793 \\
GUIDE8 & G & 25.699 & 27.090 & 3.601 \\
GUIDE8 & H & 25.652 & 27.072 & 3.698 \\
\end{tabular}
\caption{Summary of measured GFA zeropoints in terms of both ADU/s and e-/s, the latter adopting the lab-measured gains in converting from raw ADU to electrons.}
\label{tab:zps}
\end{table}
\end{center}

@@

A key assumption underlying our comparison of the measured GFA zeropoints to our zeropoint prediction is that we are using the correct GFA exposure time in computing the signal as a rate in detected electrons per second. GFA exposure times in seconds are accessed via the EXPTIME header keyword. Given the discussion about GFA timestamp oddities (e.g., [desi-commiss 2976]) and the unshuttered cameras, I decided to check how well the integration time agrees with the reported EXPTIME. It's also particularly interesting to double check EXPTIME because there are relatively few ways that the measured GFA zeropoint could be slightly \textit{deeper} than the prediction (as we have found, by 6\%), but one such possibility is that the true GFA integration time is longer than what we are assuming based on the reported GFA EXPTIME values.

To address this, I measured the length of star trails in the 5 second untracked exposure EXPID = 24467 at zenith. I find an average trail length in GUIDE2 and GUIDE7 of 62.4 asec. For comparison, the length of the sidereal day and Dec give me a prediction of 63.8 asec trails during 5 seconds. So the prediction is 2.3\% larger than the measurement. This could certainly be within the error margin of my measurement, but the agreement would be better if I assumed that EXPTIME is equal to the integration time plus the $\sim$100 ms time to shift the active image area's charge rather than simply the integration time (0.1 s / 5 s = 2\%). Regardless, this seems like quite good agreement, and any issue at the $\sim$100 ms level would result in a negligible change to my derived zeropoints, which are based on images with relatively long 30-60 second exposure times.

@@

Appended below is the full set of per-exposure, per-camera, per-amp scatter plots of GFA instrumental magnitudes versus PS1 $r$ band AB magnitudes for the set of exposures used during this study.
